Machine Learning guided workflow for Ribosome Binding Site engineering

### 2021-04-27 paper/main.tex
Updated paper.

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[maxcitenames=1,style=numeric]{biblatex}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{tcolorbox}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{thmtools}
\usepackage{thm-restate}
\usepackage{enumerate}
\usepackage{xcolor}
\usepackage{textgreek}
\usepackage{caption}
\usepackage{subcaption}
% \usepackage{subfigure}

@@

\title{Machine Learning guided workflow for Ribosome Binding Site engineering}
\author{Zhang M., Holowko M. B., Hayman Zumpe H., Ong, C. S.}
\date{\today{}}

@@

\section{Summary}

@@

\section{Contributions}
Zhang M. and Ong C. S. designed and implemented the machine learning algorithms and workflow. Holowko M. B. and Hayman Zumpe H. have designed and performed the laboratory experiments. All authors analysed the data and contributed to and reviewed the manuscript.

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[maxcitenames=1,style=numeric]{biblatex}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{tcolorbox}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{thmtools}
\usepackage{thm-restate}
\usepackage{enumerate}
\usepackage{xcolor}
\usepackage{textgreek}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{authblk}
% \usepackage{subfigure}

@@

\title{Machine Learning guided workflow for Ribosome Binding Site engineering}

\author[1,2]{Zhang M.}
\author[3]{Holowko M. B.}
\author[3]{Hayman Zumpe H.}
\author[1]{Ong, C. S.}
\affil[1]{AIML FSP}
\affil[2]{ANU}
\affil[3]{CSIRO Synthetic Biology Future Science Platform, CSIRO Land and Water, Brisbane, QLD 4102, Australia}

\date{\today{}}

@@

\section{Discussion}

@@

\section*{Contributions}
Zhang M. and Ong C. S. designed and implemented the machine learning algorithms and workflow. Holowko M. B. and Hayman Zumpe H. have designed and performed the laboratory experiments. All authors analysed the data and contributed to and reviewed the manuscript.

\section*{Competing interests}
The authors declare no competing interests

\section*{Acknowledgments}
The authors would like to acknowlege CSIRO's AI/ML and Synthetic Biology Future Science Platforms for providing funding for this research.
